### 2014-06-03 ACL2014/intro.tex
small edits to expts

 \section{Introduction}
Every day, 
hundreds of millions of users visit commercial search engines to pose
queries on topics of their interest.  
Such queries are typically just a few key words intended to specify
the topic that the user has in mind. 
To provide users with a high quality service, 
search engines such as Bing, Google, and Yahoo require
intelligent analysis to realize users' implicit intents.
The key resource that they have to help tease out what is meant is
their large history of requests, in the form of large scale query logs.  
A key primitive in 
%One of the key interesting tasks involved in 
learning users' implicit intents is the computation of 
nearest neighbors (queries) for a user given query. 
Computing nearest neighbors is useful for 
many search-related problems on the Web and the Mobile such as 
finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
and diversifying search results \cite{Song11SIGIR}; and many Natural Language Processing (NLP) tasks   
such as paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.

In this paper, we focus on the problem of finding nearest neighbors
for a given query from very large scale query logs available from a commercial search engine. 
%In order to understand the implicit users' intent, each query is initially represented in a high dimensional feature space,
%where each dimension corresponds to a clicked url.
Given the importance of this question, it is critical to design
algorithms that can scale to many queries over huge logs, and allow
online and offline computation. 
However, computing nearest neighbors of a query 
%from large-scale query logs is a non-trivial task 
can be very costly. 
Naive solutions that involve a linear search of the set of possibilities
are simply infeasible in these settings. 
%due to the computational complexity among hundreds of millions of  queries.
%The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
%linear number of comparisons in the query dataset size. For finding neighbors for hundreds of millions of queries, 
%it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
Even though distributed computing environments such as Hadoop
make it feasible to store and search large data sets in parallel, 
%Note that even in a distributed computing environment such as Hadoop,
%the
the naive pairwise computation is still infeasible. 
The reason is that the total amount of work performed is still huge,
and simply throwing more resources at the problem is not effective. 
Given a log of hundreds of millions queries, most are ``far'' from a
query of interest, and we should aim to avoid doing many ``useless''
comparisons that confirm that queries are indeed far from it. 
% from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries. In other words, even though the big \textit{O} notation is denoted as linear, \textit{2000*N} comparisons are not feasible when \textit{N} reaches to hundreds of millions.

>>>>

 \section{Introduction}
Every day, 
hundreds of millions of users visit commercial search engines to pose
queries on topics of their interest.  
Such queries are typically just a few key words intended to specify
the topic that the user has in mind. 
To provide users with a high quality service, 
search engines such as Bing, Google, and Yahoo require
intelligent analysis to realize users' implicit intents.
The key resource that they have to help tease out the intent is
their large history of requests, in the form of large scale query logs, as well
as the log of user actions on the corresponding result pages. 
A key primitive in 
%One of the key interesting tasks involved in 
learning users' implicit intents is the computation of 
nearest neighbors (queries) for a user given query. 
Computing nearest neighbors is useful for 
many search-related problems on the Web and the Mobile such as 
finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
and diversifying search results \cite{Song11SIGIR}; and many other Natural Language Processing (NLP) tasks   
such as paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
calculating distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.

In this paper, we focus on the problem of finding nearest neighbors
for a given query from very large scale query logs available from a commercial search engine. 
%In order to understand the implicit users' intent, each query is initially represented in a high dimensional feature space,
%where each dimension corresponds to a clicked url.
Given the importance of this question, it is critical to design
algorithms that can scale to many queries over huge logs, and allow
online and offline computation. 
However, computing nearest neighbors of a query 
%from large-scale query logs is a non-trivial task 
can be very costly. 
Naive solutions that involve a linear search of the set of possibilities
are simply infeasible in these settings. 
%due to the computational complexity among hundreds of millions of  queries.
%The reason being conducting pairwise computations between a given query and all the queries in the dataset involves 
%linear number of comparisons in the query dataset size. For finding neighbors for hundreds of millions of queries, 
%it means doing petabytes of comparisons; that is computationally challenging or infeasible even in a distributed setting (such as Hadoop). 
Even though distributed computing environments such as Hadoop
make it feasible to store and search large data sets in parallel, 
%Note that even in a distributed computing environment such as Hadoop,
%the
the naive pairwise computation is still infeasible. 
The reason is that the total amount of work performed is still huge,
and simply throwing more resources at the problem is not effective. 
Given a log of hundreds of millions queries, most are ``far'' from a
query of interest, and we should aim to avoid doing many ``useless''
comparisons that only confirm that other queries are indeed far from it. 
% from our experiments  using 2000 random queries to attempt to retrieve neighbors from the query logs consisting of hundreds of millions of queries. In other words, even though the big \textit{O} notation is denoted as linear, \textit{2000*N} comparisons are not feasible when \textit{N} reaches to hundreds of millions.
